The Role of Shallow Processing in Agreement Attraction

### 2020-01-03 agremeent_draft_dec17/draft_dec17.Rnw
XXXs are done

\abstract{We report the results of two speeded acceptability judgment experiments in Turkish. We hypothesized an alternative explanation for agreement attraction effects in Turkish that is based on shallow processing. Our findings contradict our hypothesized form-driven processing strategy and support an account of agreement attraction based on the use of abstract linguistic features, rather than mere form.}
\input{settings.tex}
\begin{document}

@@

section{Introduction} \label{sec:Intro}
\footnote{\printglossaries}. % add this to somewhere in the first page I suppose
\subsection{Agreement Attraction Thingy} \label{sec:Intro:literature}
\subsubsection{Morphophonology} \label{sec:Intro:literature:morphophonology}
%fill here accordingly to your results AFTER YOU WRITE THE RESULT.

@@

\subsubsection{This work details} \label{sec:Intro:literature:thiswork}
% \citet{LagoEtAl:2018} hypothesize that genitive NPs can trigger agreement attraction in Turkish, because Turkish makes heavy use of genitive subjects, which means genitives are a priori likely to function as agreement controllers. The underlying assumption is that agreement processes rely on, at least partially, the case of an NP to determine its fit for the role of an agreement controller. 
% If that is so, their items are problematic %as in ... give an example
% in that the marking on the head noun is ambiguous between possessive and accusative case, while only possessive-marked NPs qualify as agreement controllers. Therefore, if engaged in shallow processing, readers may be more likely to misidentify the genitive NP as the agreement controller when the head noun, which is the only other alternative, is ambiguous, compared to when it is not.

@@

\section{Experiment 1} \label{sec:exp1}
% do not do this in one chunk. differentiate the chunks and give them proper names.
<<>>=
fname_data <- "../workspace_exp1/exp_data.rds"
data_exp1 <- readRDS(file = fname_data)
fname_form <- "../workspace_exp1/exp_form.rds"
form_exp1 <- readRDS(file = fname_form)
form_exp1[106,2] = 18 # manually changed on sekiz to 18

@@

One hundred seven native speakers of Turkish (\textit{X} male, \textit{Y} female) in Experiment 1. The mean age is \Sexpr{mean(as.numeric(as.character(form_exp1$Age)))} , ranging from \Sexpr{min(as.numeric(as.character(form_exp1$Age)))} to \Sexpr{max(as.numeric(as.character(form_exp1$Age)))}. Experiments in this paper were carried out following the Declaration of Helsinki and the regulations concerning ethics in research in Bo\u{g}azi\c{c}i University. All participants provided informed consent. They were tested online, on IbexFarm, using their preferred platform,

@@

In Experiment 1, participants first saw sentences word by word in the middle of their screen. As in \citet{LagoEtAl:2018} study, we used 40 sets of item and manipulated the grammaticality of the sentences (\textit{grammatical} x \textit{ungrammatical}) and the number of the attractor noun (\textit{singular} x \textit{plural}). All experimental sentences followed the following template: \textit{Noun$_{\Gen}$-Noun$_{\Poss}$-Adverb-Verb}. The distribution of the verb types followed the same pattern as in \citet{LagoEtAl:2018}, namely twenty unergatives, eighteen unaccusatives, and two optionally transitive verbs. The matrix verb was marked with overt plural marker \textit{-lar} in the half of experimental items. Adverbials in our experimental sentences were always pre-verbal and contained 2-3 words consisting of 15 characters on average. The second noun phrase is the head noun of the subject in all of our experimental sentences whereas the first noun phrase is the genitive modifier of the head, thus \textit{the attractor}. Unlike \citet{LagoEtAl:2018}, our head nouns were vowel-ending, which enables us to distinguish between accusative (\textit{-yI}) and possessive (\textit{-sI}). This change was due to the morpho-phonologic nature of possessive suffix in Turkish, which spell-outs as (\textit{-I}) after a consonant same as the accusative. While all of the head nouns were singular, the attractor noun was in its plural form in the half of the experimental items. One example set of experimental items can be seen in \ref{item:exp1ExperimentalItems}.

% there may be a better way of displaying items.
\ex. \label{item:exp1ExperimentalItems}
\a. \textit{Plural Attractor, Ungrammatical Verb} \label{item:exp1expitem-plpl}\\ 
\gll *Yönetici-ler-in aşcı-sı mutfak-ta sürekli zıpl-ıyor-lar.\\ 
manager-\Pl{}-\Gen{}  cook-\Poss{} kitchen-\Loc{} non-stop  jump-\Prog{}-\Pl{}.\\
\glt `The cooks of the manager were jumping in the kitchen non-stop.' 
\b. \textit{Singular Attractor, Ungrammatical Verb} \label{item:exp1expitem-sgpl}\\ 
\gll *Yönetici-nin aşcı-sı mutfak-ta sürekli zıpl-ıyor-lar.\\ 
manager-\Gen{}  cook-\Poss{} kitchen-\Loc{} non-stop  jump-\Prog{}-\Pl{}.\\
\glt `The cook of the manager were jumping in the kitchen non-stop.'
\c. \textit{Plural Attractor, Grammatical Verb} \label{item:exp1expitem-plsg}\\ 
\gll Yönetici-ler-in aşcı-sı mutfak-ta sürekli zıpl-ıyor.\\ 
manager-\Pl{}-\Gen{}  cook-\Poss{} kitchen-\Loc{} non-stop  jump-\Prog{}.\\
\glt `The cooks of the manager was jumping in the kitchen non-stop.'
\d. \textit{Singular Attractor, Grammatical Verb}\label{item:exp1expitem-sgsg}\\ 
\gll Yönetici-nin aşcı-sı mutfak-ta sürekli zıpl-ıyor. \\ 
manager-\Gen{}  cook-\Poss{} kitchen-\Loc{} non-stop  jump-\Prog{}.\\
\glt `The cook of the manager was jumping in the kitchen non-stop.'

As for the filler sentences, we have included forty sentences, half of which ends in singular and ungrammatical while the other half was plural and grammatical. These decisions were made due to the non-existence of such sentences in the experimental sentences. We wanted to rule out a possible task strategy where participants decide on the grammaticality of the sentence by merely checking the final plural marking. Even though filler items did not follow a strict template as the experimental items, they were created within a template of \textit{Noun$_{\Gen}$-Noun$_{\Poss}$-Converb-Noun-Adverb-Verb}. The ungrammaticality was created non-locally in the filler items to avoid task strategies. Example filler sentences can be seen in \ref{item:exp1FillerItems}.

\ex. \label{item:exp1FillerItems}
\a. \textit{Plural Grammatical Verb}\\ 
\gll Sosyolog-un öğrenci-si konuş-unca tutarsızlık açığ-a çıkar-dı-lar.\\ 
sociolog-\Gen{}  student-\Poss{} speak-\Nmlz{} inconsistency  open-\Dat{} deduct-\Pst{}-\Pl{}.\\
\glt `When the sociolog's student talked, they exposed an inconsistency.' 
\b. \textit{Singular Ungrammatical Verb}\\ 
\gll *Dansöz-ün koca-sı var-ınca kapı sakince aç-tı.\\ 
dancer-\Gen{}  husband-\Poss{} arrive-\Nmlz{} door slowly  open-\Pst{}.\\
\glt Intended:`When the husband of the dancer came, the door opened slowly.'

@@

Prior to the experiments, participants gave information regarding themselves and consent to participate in the experiment. They read the instructions where we showed what they will see in the experiment, and where we informed them to give quick and accurate answers during the experiment. They are also informed regarding the that there will be a time-limit in answering the question. Every session started with a practice session where participants have been informed to be a bit faster when they were not. The sentences were presented in the middle of the screen word-by-word on a web-based platform Ibex Farm (\url{http://spellout.net/ibexfarm/}). Each word was displayed with XX font size and stayed on the screen for 300 ms, unlike \citet{LagoEtAl:2018} and \citet{WagersEtAl:2009} where words stayed for 500 ms in the screen. After the sentence is completed, participants were asked: "How did they find the sentence?" They were informed to press P on their keyboard for \textit{good} and Q for bad. Apart from the practice items, we did not provide any feedback regarding their answers. However, participants were instructed to be faster when they waited more than 5,000 ms to answer the acceptability question.

@@

\autoref{fig:exp1AvgResponse} shows the average proportions of ‘acceptable’ responses by experimental condition for both the original experiment in \citet{LagoEtAl:2018} and our replication with unambiguous possessive marking. It shows that ungrammatical sentences with plural attractors are rated as acceptable more often than their counterparts with singular attractors. In addition to ungrammatical conditions, accuracy rates within the grammatical conditions were comparable and high across conditions (mean = x\%, SE = x\%). As seen in \autoref{fig:exp1AvgResponse}, participants judged the sentences with plural attractor and singular verbs to be grammatical with the rate of X\%, which is in line with the findings reported in \citet{LagoEtAl:2018}.

<<exp1AvgResponse, fig.cap='Percentage of \\emph{yes} (acceptable) responses of Experiment 1 and \\citet{LagoEtAl:2018}', fig.height=3, fig.align='center'>>=

@@

avg_exp <- avg_clean %>% lapply(function(df) { df %>% subset(is.na(source) | source != "filler") })
avg_fillers <- avg_clean %>% lapply(function(df) { df %>% subset(source == "filler") })

p_avg_resp <- avg_exp$resp %>%
              ggplot(aes(grammatical, M, #linetype = attractor_num, 
                         color = attractor_num, group = attractor_num)) + 
                geom_point() + geom_line() + 
                facet_wrap(~experiment)

p_avg_resp <- p_avg_resp + geom_errorbar(aes(ymin = M - 1.96*SE, ymax = M + 1.96*SE), width = 0.1)

@@

p_avg_resp <- p_avg_resp + theme( strip.background = element_rect(fill="white") ) +
                           theme_bw() + xlab("") + ylab("Percentage 'acceptable'")
p_avg_resp <- p_avg_resp + scale_y_continuous(labels=scales::percent)#, breaks = c(0, .25, .5, .75, 1))
p_avg_resp <- p_avg_resp + theme_bw()
p_avg_resp <- p_avg_resp + scale_color_discrete(name = "Attractor Number")
print(p_avg_resp)

if (exists("le_poster")) {
  p_avg_resp <- avg_exp$resp %>% subset(experiment == "Experiment 1") %>%
                ggplot(aes(grammatical, M, #linetype = attractor_num, 
                           color = attractor_num, group = attractor_num)) + 
                  geom_point() + geom_line() + theme( strip.background = element_rect(fill="white")) +
                  facet_wrap(~experiment)

  p_avg_resp <- p_avg_resp + geom_errorbar(aes(ymin = M - 1.96*SE, ymax = M + 1.96*SE), width = 0.1)

  p_avg_resp <- p_avg_resp + theme( strip.background = element_rect(fill="white") ) +
                             theme_bw() + xlab("") + ylab("Percentage 'acceptable'")
  p_avg_resp <- p_avg_resp + scale_y_continuous(labels=scales::percent, limits = c(0,1))#, breaks = c(0, .25, .5, .75, 1))
  p_avg_resp <- p_avg_resp + theme_bw()
  p_avg_resp <- p_avg_resp + scale_color_discrete(name = "Attractor Number")
  ggsave(filename = "./plots_le/exp1.jpeg", p_avg_resp, height = 2.5, width = 2.5*2)
}

@@

The estimates and 95\% CIs of a Bayesian GLM in \autoref{fig:exp1ResponseModel} confirm the observations we stated above: the positive interaction between sentence grammaticality and attractor number is in line with a larger effect of attractor number in ungrammatical sentences. The main effect of ungrammaticality was XX in log-odds, and the interaction between the ungrammaticality and plural attractor was XX in log-odds. Since other estimates' credible intervals range over zero, we conclude that they were not informative. %maybe speak with p values? 
% we did not do any nested analysis, should we? Should it say anything different than figure 2?

@@

fname_exp1_responses_minimal <- "../workspace_exp1/model_responses_minimal"
m_responses_minimal <- brm(ResponseYes ~ (cEndsInConsonant + cUngrammatical + cAttractorPlural)^2 + 
                                         (cUngrammatical * cAttractorPlural + 1| subject) +
                                         (cUngrammatical * cAttractorPlural + 1| item),
                   data = df_merged_nofillers,
                   family = bernoulli("probit"),
                   file = fname_exp1_responses_minimal, 
                   chains = n_chains, cores = n_cores, iter = n_iter)

@@

if (exists("le_poster"))
{
  fname_exp1_responses <- "../workspace_exp1/model_responses_justexp1"
  m_responses_exp1 <- brm(ResponseYes ~ cUngrammatical * cAttractorPlural + 
                                 (cUngrammatical * cAttractorPlural + 1| subject) +
                                 (cUngrammatical * cAttractorPlural + 1| item),
                   data = df_merged_nofillers %>% subset(experiment == "Experiment 1"),
                   family = bernoulli("probit"),
                   file = fname_exp1_responses, 
                   chains = n_chains, cores = n_cores, iter = n_iter)

}

@@

if (exists("le_poster"))
{
    p_m_response_exp1 <- 
      create_model_coefs_plot( m_responses_exp1, 
            plot_stats = T, map_names = contrast_names,
            expand_right = 2.5, expand_top = 5, x_stat_adjust = 1.1,
            x_breaks = c(-3,-2,-1, 0,1, 2) ) + 
            xlab("Estimate (log-odds)")

    p_m_response_exp1 <- p_m_response_exp1 + annotate(x=-3, xend=2, y=0, yend=0, lwd=0.25, geom="segment")

    ggsave(filename = "./plots_le/m_exp1.jpeg", p_m_response_exp1, height = 1.5, width = 2.5*2)
}
@

@@

\begin{figure}[h]
    \centering
    \includegraphics[width=0.8\textwidth]{example-grid-100x100pt} 
    \caption{Proposed multinomial processing tree of how people judge sentences in an agreement attraction task}
    \label{fig:mptModel}
\end{figure}

@@

Eighty native speakers of Turkish (\textit{X} male, \textit{Y} female) in Experiment 1. The mean age is \textit{Z}, ranging from \textit{Z1} to \textit{Z2}. Experiments in this paper were carried out following the Declaration of Helsinki and the regulations concerning ethics in research in Bo\u{g}azi\c{c}i University. All participants provided informed consent. They were tested online, on IbexFarm, using their preferred platform, % Find citation for using IbexFarm and online testing etc?

\ex. \label{item:exp2ExperimentalItems}
\a. \textit{Plural Attractor, Ungrammatical Verb}\\ 
\gll *Tut-tuk-lar-ı aşcı mutfak-ta sürekli zıpl-ıyor-lar.\\ 
hire-\Nmlz{}-\Pl{}-\Poss{}  cook kitchen-\Loc{} non-stop  jump-\Prog{}-\Pl{}.\\
\glt `The cook that they hired were jumping in the kitchen non-stop.' 
\b. \textit{Singular Attractor, Ungrammatical Verb}\\ 
\gll *Tut-tuğ-u aşcı mutfak-ta sürekli zıpl-ıyor-lar.\\ 
hıre-\Nmlz{}-\Poss{}  cook kitchen-\Loc{} non-stop  jump-\Prog{}-\Pl{}.\\
\glt `The cook that they hired were jumping in the kitchen non-stop.'
\c. \textit{Plural Attractor, Grammatical Verb}\\ 
\gll Tut-tuk-lar-ı aşcı mutfak-ta sürekli zıpl-ıyor.\\ 
hire-\Nmlz{}-\Pl{}-\Poss{}  cook kitchen-\Loc{} non-stop  jump-\Prog{}.\\
\glt `The cook that they hired was jumping in the kitchen non-stop.'
\d. \textit{Singular Attractor, Grammatical Verb}\\ 
\gll Tut-tuğ-u aşcı mutfak-ta sürekli zıpl-ıyor.\\ 
hıre-\Nmlz{}-\Poss{}  cook kitchen-\Loc{} non-stop  jump-\Prog{}.\\
\glt `The cook that they hired was jumping in the kitchen non-stop.'

In our filler items for Experiment 2, we made sure that every sentence starts with an object relative clause. We used plural distractors with grammatical verbs and singular distractors with ungrammatical verbs. In all of our filler sentences, the dependency between the first NP subject and its verb resolved in an adverbial embedded sentence. Grammatical filler items in Experiment 2 all had a template of \textit{RC$_{\Pl{}}$-Bare Noun-Adverb-Converb-Noun-Adverb-Verb$_{\Pl{}}$}, whereas ungrammatical filler items used a template of \textit{RC$_{\Sg{}}$-Bare Noun-Adverb-Converb-Noun-Adverb-Verb$_{\Sg{}}$}

\ex. \label{item:exp2FillerItems}
\a. \textit{Plural Grammatical Verb}\\ 
\gll Oku-t-tuk-lar-ı öğrenci başarılı ol-unca mutlu ol-du-lar.\\ 
read-\Caus{}-\Nmlz{}-\Pl{}-\Poss{}  student successful be-\Nmlz{} happy be-\Pst{}-\Pl{}.\\
\glt `When the student they sponsored become successful, they became happy.' 
\b. \textit{Singular Ungrammatical Verb}\\ 
\gll *Kandır-dığ-ı adam öde-me-yince bulaşık saatlerce yıka-dı.\\ 
trick-\Nmlz{}-\Poss{}  man pay-\Neg{}-\Nmlz{} dish for.hours clean-\Pst{}.\\
\glt Intended:`When the man he tricked did not pay, he cleaned dishes for hours.'

<<loadExperiment2Data>>=
fname_data2 <- "../workspace_exp2/exp_data.rds"
data_exp2 <- readRDS(file = fname_data2)

@@

df_merged2_nonna <- df_merged2 %>% subset(!is.na(ResponseYes))
@

@@

if (exists("le_poster")) {

>>>>

\abstract{We report the results of two speeded acceptability judgment experiments in Turkish. We hypothesized an alternative explanation for agreement attraction effects in Turkish that is based on shallow processing. Our findings contradict our hypothesized form-driven processing strategy and support an account of agreement attraction based on the use of abstract linguistic features, rather than mere form.}

\input{settings.tex}

\begin{document}

@@

\section{Introduction} \label{sec:Intro}

%\footnote{\printglossaries}. % add this to somewhere in the first page I suppose

\subsection{Agreement Attraction Thingy} \label{sec:Intro:literature}

\subsubsection{Morphophonology} \label{sec:Intro:literature:morphophonology}

%fill here accordingly to your results AFTER YOU WRITE THE RESULT.

@@

\subsubsection{This work details} \label{sec:Intro:literature:thiswork}

% \citet{LagoEtAl:2018} hypothesize that genitive NPs can trigger agreement attraction in Turkish, because Turkish makes heavy use of genitive subjects, which means genitives are a priori likely to function as agreement controllers. The underlying assumption is that agreement processes rely on, at least partially, the case of an NP to determine its fit for the role of an agreement controller. 
% If that is so, their items are problematic %as in ... give an example
% in that the marking on the head noun is ambiguous between possessive and accusative case, while only possessive-marked NPs qualify as agreement controllers. Therefore, if engaged in shallow processing, readers may be more likely to misidentify the genitive NP as the agreement controller when the head noun, which is the only other alternative, is ambiguous, compared to when it is not.

@@

\section{Experiment 1} \label{sec:exp1}

% do not do this in one chunk. differentiate the chunks and give them proper names.
<<>>=
fname_data <- "../workspace_exp1/exp_data.rds"
data_exp1 <- readRDS(fname_data)
fname_form <- "../workspace_exp1/exp_form.rds"
form_exp1 <- readRDS(file = fname_form)
form_exp1[106,2] = 18 # manually changed on sekiz to 18

@@

One hundred seven native speakers of Turkish in Experiment 1. The mean age is \Sexpr{mean(as.numeric(as.character(form_exp1$Age)))}, ranging from \Sexpr{min(as.numeric(as.character(form_exp1$Age)))} to \Sexpr{max(as.numeric(as.character(form_exp1$Age)))}. Across participants, a total \Sexpr{sum(is.na(df_exp1_na_nofillers$ResponseYes))} items were not responded to before the 5 second deadline by \Sexpr{length(unique(df_exp1_na_nofillers$subject))} different participants. These items were not included in the analysis. Experiments in this paper were carried out following the Declaration of Helsinki and the regulations concerning ethics in research in Bo\u{g}azi\c{c}i University. All participants provided informed consent. They were tested online, on IbexFarm, using their preferred platform.

@@

In Experiment 1, participants first saw sentences word by word in the middle of their screen. As in \citet{LagoEtAl:2018} study, we used 40 sets of item and manipulated the grammaticality of the sentences (\textit{grammatical} x \textit{ungrammatical}) and the number of the attractor noun (\textit{singular} x \textit{plural}). All experimental sentences followed the following template: \textit{Noun$_{{\textsc{gen}}}$-Noun$_{{\textsc{poss}}}$-Adverb-Verb}. The distribution of the verb types followed the same pattern as in \citet{LagoEtAl:2018}, namely twenty unergatives, eighteen unaccusatives, and two optionally transitive verbs. The matrix verb was marked with overt plural marker \textit{-lar} in the half of experimental items. Adverbials in our experimental sentences were always pre-verbal and contained 2-3 words consisting of 15 characters on average. The second noun phrase is the head noun of the subject in all of our experimental sentences whereas the first noun phrase is the genitive modifier of the head, thus \textit{the attractor}. Unlike \citet{LagoEtAl:2018}, our head nouns were vowel-ending, which enables us to distinguish between accusative (\textit{-yI}) and possessive (\textit{-sI}). This change was due to the morpho-phonologic nature of possessive suffix in Turkish, which spell-outs as (\textit{-I}) after a consonant same as the accusative. While all of the head nouns were singular, the attractor noun was in its plural form in the half of the experimental items. One example set of experimental items can be seen in \ref{item:exp1ExperimentalItems}.

% there may be a better way of displaying items.
\ex. \label{item:exp1ExperimentalItems}
\a. \textit{Plural Attractor, Ungrammatical Verb} \label{item:exp1expitem-plpl}\\ 
\gll *Yönetici-ler-in aşcı-sı mutfak-ta sürekli zıpl-ıyor-lar.\\ 
manager-\textsc{pl}-\textsc{gen}  cook-\textsc{poss} kitchen-\textsc{loc} non-stop  jump-\textsc{prog}-\textsc{pl}.\\
\glt `The cooks of the manager were jumping in the kitchen non-stop.' 
\b. \textit{Singular Attractor, Ungrammatical Verb} \label{item:exp1expitem-sgpl}\\ 
\gll *Yönetici-nin aşcı-sı mutfak-ta sürekli zıpl-ıyor-lar.\\ 
manager-\textsc{gen}  cook-\textsc{poss} kitchen-\textsc{loc} non-stop  jump-\textsc{prog}-\textsc{pl}.\\
\glt `The cook of the manager were jumping in the kitchen non-stop.'
\c. \textit{Plural Attractor, Grammatical Verb} \label{item:exp1expitem-plsg}\\ 
\gll Yönetici-ler-in aşcı-sı mutfak-ta sürekli zıpl-ıyor.\\ 
manager-\textsc{pl}-\textsc{gen}  cook-\textsc{poss} kitchen-\textsc{loc} non-stop  jump-\textsc{prog}.\\
\glt `The cooks of the manager was jumping in the kitchen non-stop.'
\d. \textit{Singular Attractor, Grammatical Verb}\label{item:exp1expitem-sgsg}\\ 
\gll Yönetici-nin aşcı-sı mutfak-ta sürekli zıpl-ıyor. \\ 
manager-\textsc{gen}  cook-\textsc{poss} kitchen-\textsc{loc} non-stop  jump-\textsc{prog}.\\
\glt `The cook of the manager was jumping in the kitchen non-stop.'

As for the filler sentences, we have included forty sentences, half of which ends in singular and ungrammatical while the other half was plural and grammatical. These decisions were made due to the non-existence of such sentences in the experimental sentences. We wanted to rule out a possible task strategy where participants decide on the grammaticality of the sentence by merely checking the final plural marking. Even though filler items did not follow a strict template as the experimental items, they were created within a template of \textit{Noun$_{{\textsc{gen}}}$-Noun$_{{\textsc{gen}}}$-Converb-Noun-Adverb-Verb}. The ungrammaticality was created non-locally in the filler items to avoid task strategies. Example filler sentences can be seen in \ref{item:exp1FillerItems}.

\ex. \label{item:exp1FillerItems}
\a. \textit{Plural Grammatical Verb}\\ 
\gll Sosyolog-un öğrenci-si konuş-unca tutarsızlık açığ-a çıkar-dı-lar.\\ 
sociolog-\textsc{gen}  student-\textsc{poss} speak-\textsc{nmlz} inconsistency  open-\Dat{} deduct-\textsc{pst}-\textsc{pl}.\\
\glt `When the sociolog's student talked, they exposed an inconsistency.' 
\b. \textit{Singular Ungrammatical Verb}\\ 
\gll *Dansöz-ün koca-sı var-ınca kapı sakince aç-tı.\\ 
dancer-\textsc{gen}  husband-\textsc{poss} arrive-\textsc{nmlz} door slowly  open-\textsc{pst}.\\
\glt Intended:`When the husband of the dancer came, the door opened slowly.'

@@

Prior to the experiments, participants gave information regarding themselves and consent to participate in the experiment. They read the instructions where we showed what they will see in the experiment, and where we informed them to give quick and accurate answers during the experiment. They are also informed regarding the that there will be a time-limit in answering the question. Every session started with a practice session where participants have been informed to be a bit faster when they were not. The sentences were presented in the middle of the screen word-by-word on a web-based platform Ibex Farm (\url{http://spellout.net/ibexfarm/}). Each word was displayed with 30 font size and stayed on the screen for 300 ms, unlike \citet{LagoEtAl:2018} and \citet{WagersEtAl:2009} where words stayed for 500 ms in the screen. After the sentence is completed, participants were asked: "How did they find the sentence?" They were informed to press P on their keyboard for \textit{good} and Q for bad. Apart from the practice items, we did not provide any feedback regarding their answers. However, participants were instructed to be faster when they waited more than 5,000 ms to answer the acceptability question.

@@

@@

avg_exp <- avg_clean %>% lapply(function(df) { df %>% subset(is.na(source) | source != "filler") })
avg_fillers <- avg_clean %>% lapply(function(df) { df %>% subset(source == "filler") })
pd <- position_dodge(0.1)
p_avg_resp <- avg_exp$resp %>%
              ggplot(aes(grammatical, M, #linetype = attractor_num, 
                         color = attractor_num, group = attractor_num)) + 
                geom_point(position = pd) + geom_line(position = pd) + 
                facet_wrap(~experiment)

p_avg_resp <- p_avg_resp + geom_errorbar(aes(ymin = M - 1.96*SE, ymax = M + 1.96*SE), width = 0.1, position = pd)

@@

p_avg_resp <- p_avg_resp + theme( strip.background = element_rect(fill="white") ) +
                           theme_bw() + xlab("") + ylab("Percentage 'acceptable'")
p_avg_resp <- p_avg_resp + scale_y_continuous(labels=scales::percent)#, breaks = c(0, .25, .5, .75, 1))
p_avg_resp <- p_avg_resp + theme_bw()
p_avg_resp <- p_avg_resp + scale_color_discrete(name = "Attractor Number")

@@

\autoref{fig:exp1AvgResponse} shows the average proportions of ‘acceptable’ responses by experimental condition for both the original experiment in \citet{LagoEtAl:2018} and our replication with unambiguous possessive marking. It shows that ungrammatical sentences with plural attractors are rated as acceptable more often (M = \Sexpr{avg_exp$resp$M[3]}\%, SE = \Sexpr{avg_exp$resp$SE[3]}\%) than their counterparts with singular attractors (M=\Sexpr{avg_exp$resp$M[4]}\%, SE=\Sexpr{avg_exp$resp$SE[4]}\%). In addition to ungrammatical conditions, accuracy rates within the grammatical conditions were comparable and high across conditions (M = \Sexpr{avg_exp$resp$M[1]}\% and \Sexpr{avg_exp$resp$M[2]}\%, SE = \Sexpr{avg_exp$resp$SE[1]}\% and \Sexpr{avg_exp$resp$SE[2]}\% for singular and plural attractors respectively). As seen in \autoref{fig:exp1AvgResponse}, participants judged the sentences with plural attractor and singular verbs to be grammatical with the rate of \Sexpr{avg_exp$resp$M[3]-avg_exp$resp$M[4]}\%, which is in line with the findings reported in \citet{LagoEtAl:2018}.

<<exp1AvgResponse, fig.cap='Percentage of \\emph{yes} (acceptable) responses of Experiment 1 and \\citet{LagoEtAl:2018}', fig.height=3, fig.align='center'>>=
print(p_avg_resp)

<<exp1models, include=FALSE>>=

@@

fname_exp1_responses_minimal <- "../workspace_exp1/model_responses_minimal"
m_responses_minimal <- brm(ResponseYes ~ (cEndsInConsonant + cUngrammatical + cAttractorPlural)^2 + 
                                         (cUngrammatical * cAttractorPlural + 1| subject) +
                                         (cUngrammatical * cAttractorPlural + 1| item),  #Can we omit this one out? We do not have every condition for every item from each subject? It goes to minus infinity.
                   data = df_merged_nofillers,
                   family = bernoulli("probit"),
                   file = fname_exp1_responses_minimal, 
                   chains = n_chains, cores = n_cores, iter = n_iter)

@@

model_results_table <- fixef(m_responses, summary = T, robust = F) %>% 
  as.data.frame() %>% tibble::rownames_to_column("variables")
@

The estimates and 95\% CIs of a Bayesian GLM in \autoref{fig:exp1ResponseModel} confirm the observations we stated above: the positive interaction between sentence grammaticality and attractor number is in line with a larger effect of attractor number in ungrammatical sentences. The main effect of ungrammaticality was \Sexpr{model_results_table[3,2]}[\Sexpr{model_results_table[3,4]};\Sexpr{model_results_table[3,4]}] in log-odds, and the interaction between the ungrammaticality and plural attractor was \Sexpr{model_results_table[7,2]}[\Sexpr{model_results_table[7,4]};\Sexpr{model_results_table[7,5]}] in log-odds. Since other estimates' credible intervals range over zero, we conclude that they were not informative. %maybe speak with p values? 
% we did not do any nested analysis, should we? Should it say anything different than figure 2?

@@

@@

\begin{figure}[h]
    \centering
                      \begin{forest}
                  for tree = {
                  % nodes
                      draw, 
                      align=center,
                      minimum height=5ex,
                      minimum width=3em,
                      font=\linespread{0.84}\selectfont,
                  % tree
                      grow'=0,
                      parent anchor=east,
                      child  anchor=west,
                      s sep = 4mm,    
                      l sep = 12mm, 
                  % edge
                      edge = {semithick},
                  % level styles
                  if level = 0{}{rounded corners=2ex},
                  where n children=0{tier=level, sharp corners}{calign=edge midpoint},
                  % edge labels
                  EL/.style={edge label={node [pos=0.5, fill=white,
                                               font=\scriptsize\sffamily,
                                               inner sep=2pt] {$#1$}}
                                      }
                              }% end for tree
                  [,coordinate
                  [target\\ item,no edge
                      [recolection\\ certainity, EL=r
                          ["yes"]
                      ]
                      [recolection\\ uncertainity, EL=1-r,
                          [guess "yes", tier=L1, EL=g,
                              ["yes"]
                          ]
                          [guess "no", tier=L1, EL=1-g
                              ["no"]
                          ]
                      ]
                  ]
                  [,coordinate, no edge]
                  [target\\ item, no edge
                      [guess "yes", tier=L1, EL=g,
                              ["yes"]
                      ]
                      [guess "no", tier=L1, EL=1-g
                          ["no"]
                      ]
                   ]
                  ]
                      \end{forest} 
    \caption{Proposed multinomial processing tree of how people judge sentences in an agreement attraction task}
    \label{fig:mptModel}
\end{figure}

@@

<<loadExperiment2Data>>=
fname_data2 <- "../workspace_exp2/exp_data.rds"
data_exp2 <- readRDS(file = fname_data2)
fname_form <- "../workspace_exp2/exp_form.rds"
form_exp2 <- readRDS(file = fname_form)
form_exp2 <- form_exp2[-c(56),]

@@

df_exp2_na_nofillers <- subset(df_merged2, is.na(ResponseYes) & source != "filler")

df_merged2_nonna <- df_merged2 %>% subset(!is.na(ResponseYes))

Eighty native speakers of Turkish in Experiment 1. The mean age is \Sexpr{mean(as.numeric(as.character(form_exp2$Age)))}, ranging from \Sexpr{min(as.numeric(as.character(form_exp2$Age)))} to \Sexpr{max(as.numeric(as.character(form_exp2$Age)))}. Across participants, a total \Sexpr{sum(is.na(df_exp2_na_nofillers$ResponseYes))} items were not responded to before the 5 second deadline by \Sexpr{length(unique(df_exp2_na_nofillers$subject))} different participants. These items were not included in the analysis. Experiments in this paper were carried out following the Declaration of Helsinki and the regulations concerning ethics in research in Bo\u{g}azi\c{c}i University. All participants provided informed consent. They were tested online, on IbexFarm, using their preferred platform, % Find citation for using IbexFarm and online testing etc?

\ex. \label{item:exp2ExperimentalItems}
\a. \textit{Plural Attractor, Ungrammatical Verb}\\ 
\gll *Tut-tuk-lar-ı aşcı mutfak-ta sürekli zıpl-ıyor-lar.\\ 
hire-\textsc{nmlz}-\textsc{pl}-\textsc{poss}  cook kitchen-\textsc{loc} non-stop  jump-\textsc{prog}-\textsc{pl}.\\
\glt `The cook that they hired were jumping in the kitchen non-stop.' 
\b. \textit{Singular Attractor, Ungrammatical Verb}\\ 
\gll *Tut-tuğ-u aşcı mutfak-ta sürekli zıpl-ıyor-lar.\\ 
hıre-\textsc{nmlz}-\textsc{poss}  cook kitchen-\textsc{loc} non-stop  jump-\textsc{prog}-\textsc{pl}.\\
\glt `The cook that they hired were jumping in the kitchen non-stop.'
\c. \textit{Plural Attractor, Grammatical Verb}\\ 
\gll Tut-tuk-lar-ı aşcı mutfak-ta sürekli zıpl-ıyor.\\ 
hire-\textsc{nmlz}-\textsc{pl}-\textsc{poss}  cook kitchen-\textsc{loc} non-stop  jump-\textsc{prog}.\\
\glt `The cook that they hired was jumping in the kitchen non-stop.'
\d. \textit{Singular Attractor, Grammatical Verb}\\ 
\gll Tut-tuğ-u aşcı mutfak-ta sürekli zıpl-ıyor.\\ 
hıre-\textsc{nmlz}-\textsc{poss}  cook kitchen-\textsc{loc} non-stop  jump-\textsc{prog}.\\
\glt `The cook that they hired was jumping in the kitchen non-stop.'

In our filler items for Experiment 2, we made sure that every sentence starts with an object relative clause. We used plural distractors with grammatical verbs and singular distractors with ungrammatical verbs. In all of our filler sentences, the dependency between the first NP subject and its verb resolved in an adverbial embedded sentence. Grammatical filler items in Experiment 2 all had a template of \textit{RC$_{\textsc{pl}}$-Bare Noun-Adverb-Converb-Noun-Adverb-Verb$_{\textsc{pl}}$}, whereas ungrammatical filler items used a template of \textit{RC$_{\Sg{}}$-Bare Noun-Adverb-Converb-Noun-Adverb-Verb$_{\Sg{}}$}

\ex. \label{item:exp2FillerItems}
\a. \textit{Plural Grammatical Verb}\\ 
\gll Oku-t-tuk-lar-ı öğrenci başarılı ol-unca mutlu ol-du-lar.\\ 
read-\Caus{}-\textsc{nmlz}-\textsc{pl}-\textsc{poss}  student successful be-\textsc{nmlz} happy be-\textsc{pst}-\textsc{pl}.\\
\glt `When the student they sponsored become successful, they became happy.' 
\b. \textit{Singular Ungrammatical Verb}\\ 
\gll *Kandır-dığ-ı adam öde-me-yince bulaşık saatlerce yıka-dı.\\ 
trick-\textsc{nmlz}-\textsc{poss}  man pay-\Neg{}-\textsc{nmlz} dish for.hours clean-\textsc{pst}.\\
\glt Intended:`When the man he tricked did not pay, he cleaned dishes for hours.'

@@
